---
title: "Researcher Training and Development Sessions for 2025"
subtitle: "Joint Report from RDS & OGR Teams (Sept 30, 2025)"
#author: "Jen Beaudry"
#date: "29/09/2025"
output: pdf_document
editor_options: 
  chunk_output_type: console
header-includes:
  - \usepackage{caption}
  - \usepackage{titling}
    \setlength{\droptitle}{-2cm} # removes some of the white space above title
  - \pretitle{\begin{center}
    \includegraphics[width=1.5in, height=1.5in]{flinders-university-horizontal-master.png}\LARGE\\} # adds logo
  - \posttitle{\end{center}}
  - \usepackage{fancyhdr}
  - \fancypagestyle{plain}{\pagestyle{fancy}} # sets the footer on page 1
  - \pagestyle{fancy} # sets the footer on page 2 and beyond
  - \fancyhf{} # clears existing header & footer
  - \renewcommand{\headrulewidth}{0pt} # removes the line from the header
  - \fancyfoot[L]{Researcher Training and Development 2025} # report name in footer
  - \fancyfoot[R]{\thepage} # page number in foooter
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      include = FALSE, 
                      eval = TRUE)

```

```{r library, eval=TRUE}

# Function to load or install packages
load_or_install <- function(packages) {
  for (package in packages) {
    if (!require(package, character.only = TRUE)) {
      install.packages(package, dependencies = TRUE)
      library(package, character.only = TRUE)
    }
  }
}

# Required packages 
packages <- c("here"
              , "tidyverse"
              , "kableExtra"
              , "readxl"
              , "janitor"
              , "rmarkdown"
              , "ggrepel" #for annotations in ggplot
              , "captioner"
              )

# Load or install the packages
load_or_install(packages)

```

```{r functions}

styler_pdf <- function(dat) {
  dat %>%
     kable_styling(full_width = F, 
                latex_options = c("striped", "HOLD_position"))
}

table_nums <- captioner(prefix = "Table")
fig_nums <- captioner(prefix = "Figure")

```

<!--  This reruns the cleaning script so we don't have to run that separately when we update the data. 
  I think. Check that this works! It might only happen when we knit the file.-->

```{r run preprocessing, child=(here::here("analysis", "0. cleaning_2025_training_data.Rmd")), include=FALSE, eval=FALSE}


```

```{r load all training data}

# load data from the five files: each source separately and then the join files

# HDR data

df_hdr <- read_csv(here::here("data", "processed", "hdr_processed.csv"), lazy = FALSE) 

# ienrol RTDC data
df_ienrol <- read_csv(here::here("data", "processed", "ienrol_processed.csv"), lazy = FALSE)

# spreadsheet RTDC data
df_sp <- read_csv(here::here("data", "processed", "spreadsheet_processed.csv"), lazy = FALSE)

# joint ienrol RTDC data + HDR data
df_ienrol_hdr <- read_csv(here::here("data", "processed", "joined_ienrol_hdr_processed.csv"), lazy = FALSE)

# joint spreadsheet RTDC data + collapsed HDR data
df_sp_hdr <- read_csv(here::here("data", "processed", "joined_spreadsheet_hdr_processed.csv"), lazy = FALSE)


# we also need to bring in the youtube views; see the spreadsheet in the youtube analytics folder
youtube <- "879"

```

```{r convert to factors}

# turn them into factors because the formatting isn't saved in csv files

cols <- c("event_num",
          "course_name",
             "portfolio",
          "attendance_status",
          "role", 
          "modality",
          "training_category",
          "data_source", 
          "theme", 
          "team")

df_hdr <- df_hdr %>% 
  dplyr::mutate(across(all_of(cols), ~factor(.)))

cols <- c("event_num",
          "course_name",
             "portfolio",
          "attendance_status",
          "role", 
          "department",
          "modality",
          "data_source", 
          "team")

df_ienrol <- df_ienrol %>% 
  dplyr::mutate(across(all_of(cols), ~factor(.)))

cols <- c("event",
          "course_name",
          "modality",
          "data_source", 
          "theme", 
          "team")

df_sp <- df_sp %>% 
  dplyr::mutate(across(all_of(cols), ~factor(.)))

cols <- c("event_num",
          "course_name",
             "portfolio",
          "attendance_status",
          "role", 
          "department",
          "modality",
          "training_category",
          "data_source", 
          "theme", 
          "team")

df_ienrol_hdr <- df_ienrol_hdr %>% 
  dplyr::mutate(across(all_of(cols), ~factor(.)))

cols <- c("event",
          "course_name",
          "modality",
          "data_source", 
          "event_num",
          "theme", 
          "team")

df_sp_hdr <- df_sp_hdr %>% 
  dplyr::mutate(across(all_of(cols), ~factor(.)))

```

```{r summary stats hdr data}

# calculate number of courses from the hdr data

n_courses_hdr <- df_hdr %>% 
# filter(attendance_status == "Attended") %>% # they have 6 courses with 0 attendees
  count(course_name, event_num)

# calculate number of attendees -- we get 1840, but I think it should be 1864.
  # that's what I get when I filter just by attendance_status. When I add in
  # course_name and event_num, I lose 24 people for some reason.
# [breadcrumb. I need to figure this out. It's something to do with counting for some reason]

n_attendees_hdr <- df_hdr %>%
  filter(attendance_status == "Attended") %>% 
  count(fan, course_name, event_num)

# unique attendees 
n_unique_attendees_hdr <- n_distinct(n_attendees_hdr$fan)

# all hdr attendees broken down by College

df_portfolio_hdr <- df_hdr %>% 
  count(portfolio) %>% 
  arrange(-n)

# Attendance status

attended_hdr <- df_hdr %>% filter(attendance_status == "Attended")
not_attended_hdr <- df_hdr %>% filter(attendance_status == "Did not attend")

```

```{r summary stats ienrol data}

# calculate number of courses

n_courses_rds <- df_ienrol %>% 
  filter(attendance_status == "Attended") %>% 
  count(course_name, event_num)

# calculate number of attendees
  # this number will differ from the T&D spreadsheet because we have had attendees that are not in iEnrol

n_attendees_ienrol <- df_ienrol %>%
  filter(attendance_status == "Attended") %>% 
  count(fan, course_name, event_num)

# unique attendees 
n_unique_attendees_ienrol <- n_distinct(n_attendees_ienrol$fan)

# all attendees broken down by College

df_portfolios_ienrol <- df_ienrol %>% 
  filter (portfolio == "Other portfolios") %>% 
  count(department) %>% 
  arrange(-n)

n_portfolios_ienrol <- unique(df_portfolios_ienrol$department)

# Attendance status

attended_ienrol <- df_ienrol %>% filter(attendance_status == "Attended")
not_attended_ienrol <- df_ienrol %>% filter(attendance_status == "Did not attend")

```

```{r summary stats spreadsheet data}

# number of attendees 
  # this number will differ from the ienrol data because we have had attendees that are not in iEnrol
n_attended_sp <- sum(df_sp$attended)

# figure out how many sessions were held face-to-face vs. online & how many folks attended in person or online for hybrid events
n_event_sp <- df_sp %>% 
  filter(event == "E")

```

```{r summary stats ienrol and HDR data}

# calculate number of courses

n_courses_ienrol_hdr <- df_ienrol_hdr %>% 
 # filter(attendance_status == "Attended") %>% 
  count(course_name, event_num, modality)

n_courses_att_ienrol_hdr <- df_ienrol_hdr %>% 
  filter(attendance_status == "Attended") %>% # only include those with attendees
  count(course_name, event_num)

# calculate number of attendees
  # this number will differ from the T&D spreadsheet because we have had attendees that are not in iEnrol

n_attendees_ienrol_hdr <- df_ienrol_hdr %>%
  filter(attendance_status == "Attended") %>% 
  count(fan, course_name, event_num)

# unique attendees 
n_unique_attendees_ienrol_hdr <- n_distinct(n_attendees_ienrol_hdr$fan)

# all attendees broken down by College

df_portfolios_ienrol_hdr <- df_ienrol_hdr %>% 
  filter (portfolio == "Other portfolios") %>% 
  count(department) %>% 
  arrange(-n)

n_portfolios_ienrol_hdr <- unique(df_portfolios_ienrol_hdr$department)

# Attendance status

attended_ienrol_hdr <- df_ienrol_hdr %>% filter(attendance_status == "Attended")
not_attended_ienrol_hdr <- df_ienrol_hdr %>% filter(attendance_status == "Did not attend")

```


```{r summary stats spreadsheet and HDR data}

# number of attendees 
  # this number will differ from the T&D spreadsheet because we have had attendees that are not in iEnrol
n_attended_sp_hdr <- sum(df_sp_hdr$attended)

# I want to look at the distribution of attendees across teams
attendees_sp_hdr <- df_sp_hdr %>% 
    filter (modality == "synchronous") %>% 
  select (team, attended)


# figure out how many sessions were held face-to-face vs. online & how many folks attended in person or online for hybrid events
  # [breadcrumb: we don't have this data for HDR data. Does Dani?]
n_event_sp <- df_sp %>% 
  filter(event == "E")


```


```{r captions, eval = TRUE}

# use these to provide the captions and numbers for the figures 
# use kable captions to provide the captions for the Tables, but use the captioner package
  # to be able to reference the tables within the text

fig_nums(name = "college_attendees", 
         caption = "Number of Attendees in Training & Development Sessions (2025)")

fig_nums(name = "college_unique_attendees", 
         caption = "Number of Unique Attendees in Training & Development Sessions (2025)")

fig_nums(name = "role_attendees", 
         caption = "Number of Attendees in Training & Development Sessions (2025)")

fig_nums(name = "role_unique_attendees", 
         caption = "Number of Unique Attendees in Training & Development Sessions (2025)")

fig_nums(name = "attendee_distributions", 
         caption = "Distribution of Attendees by Team")

table_nums(name = "theme_overview", 
          caption = "Training and Development Summary for 2025")

table_nums(name = "sessions_by_theme", 
          caption = "Training and Development Sessions by Theme for 2025")

```

## Summary of Researcher Development Activities

In 2025, the two Researcher Development teams (i.e., Researcher Training, 
Development and Communication team in Research Development and Support [RDS], and 
the HDR Development team in the Office of Graduate Research [OGR]) have offered 
`r nrow(n_courses_ienrol_hdr)` information
sessions and development workshops to researchers, research support staff, and 
HDR students at Flinders University. 

From the Flinders community, `r nrow(n_attendees_ienrol_hdr)` people attended the 
research training and development sessions thus far in 2025. Our actual attendance numbers 
are larger (*n* = `r sum(df_sp_hdr$attended)`) because we allowed 
external researchers to join select sessions (e.g., Open Research sessions, 
the inaugural NADOIC Indigenous Research Showcase, etc.). 
Of the `r nrow(n_attendees_ienrol_hdr)` attendees from Flinders, 
`r n_unique_attendees_ienrol_hdr` were unique attendees, demonstrating
that a large number of people from the Flinders research community are engaging in
our research training and development program.

The number of attendees at our sessions varied from `r (min(n_courses_att_ienrol_hdr$n))` in 
some of the more bespoke HDR sessions (e.g., 3MT practice sessions, Drop-in sessions) 
to `r max(n_courses_att_ienrol_hdr$n)` in our first session on Microsoft 
CoPilot and AI for research. The mean number of attendees at 
our sessions was `r round(mean(n_courses_att_ienrol_hdr$n),0)` with a median of 
`r round(median(n_courses_att_ienrol_hdr$n),0)`.

In this report, we first break down our enrolments by College and Portfolio. We
then explore the topics of the sessions in more detail. We provide an overview
of the number of sessions and number of attendees by theme, and then
report the number of attendees in each session organised by theme.



## Number of Attendees by College and Portfolio

`r fig_nums(name = "college_attendees", display = "cite")` illustrates how many 
people attended these sessions across the Colleges and Portfolios. By far, the 
largest number of attendees were in the College of Medicine and Public Health, 
which is representative of the large number of researchers in that College.

Most of the professional staff who attended our training and development sessions 
were from the Portfolio of the Deputy Vice-Chancellor (Research). We collapsed all
other portfolios in the University into a single "Other portfolios" category
because of the large number of portfolios that our attendees represent
(including Library; Learning and Teaching Innovation; Information and Digital Services; 
Chief of Staff Portfolio; and Governance, Legal and Risk; as well as people who are not
aligned with any portfolio in the iEnrol system).

Overall, across all Colleges and Portfolios, the average attendance rate for
2025 was `r round(((nrow(attended_ienrol_hdr)/(nrow(attended_ienrol_hdr) + nrow(not_attended_ienrol_hdr)))*100), 0)`%. 

`r fig_nums(name = "college_unique_attendees", display = "cite")` illustrates the unique
number of attendees across the Colleges and Portfolios. The College of Medicine
and Public Health also had the most unique attendees.

\newpage
`r fig_nums(name = "college_attendees")`

```{r plot the ienrol attendance, include = TRUE, eval=TRUE, fig.width = 15, fig.height = 9}

# count attendees rate per portfolio
df_attend <- df_ienrol_hdr %>%
  filter(attendance_status == "Attended") %>%
  count(portfolio)


# plot it [this has attendance numbers by the portfolios]
ggplot(df_attend, aes(
  x = reorder(portfolio, n),
  y = n
)) +
  geom_bar(stat = "identity", colour = "black", fill = "#90b8da") +
  geom_text(aes(y = n,
                x = portfolio,
                label = n),
            position = position_stack(vjust = 0.5),
            size = 6) +
  coord_flip() +
  labs (#title = "Number of Attendees in Training & Development Sessions (2025)", # included in caption
        x = element_blank(),
        y = "Number of attendees") +
  theme_classic() +
  theme(
    title = element_text(size = 14, family="sans"),
    legend.text = element_text(size = 14, family="sans"),
    axis.text = element_text(size = 14, family ="sans"),
    axis.title = element_text(size = 14, family = "sans")
    ) +
  scale_fill_manual(
    values = "#90b8da"
  )
 # scale_x_discrete(
 #   labels = df_label$port_perc_label)


ggsave(plot = last_plot(),filename = here::here("figures", "2025 attendance by portfolio.png"),
       width = 15, height = 9, dpi = 300)

```

\vskip 0.3in

`r fig_nums(name = "college_unique_attendees")`

```{r plot the ienrol attendance for unique attendees, include = TRUE, eval=TRUE, fig.width = 15, fig.height = 9}

# count unique attendees per portfolio
df_attend_unique <- df_ienrol_hdr %>%
  filter(attendance_status == "Attended") %>%
  distinct(fan, attendance_status, portfolio) %>%
  count(portfolio)


# plot it [this has unique attendance numbers by the portfolios]
ggplot(df_attend_unique, aes(
  x = reorder(portfolio, n),
  y = n
)) +
  geom_bar(stat = "identity", colour = "black", fill = "#90b8da") +
  geom_text(aes(y = n,
                x = portfolio,
                label = n),
            position = position_stack(vjust = 0.5),
            size = 6) +
  coord_flip() +
  labs (#title = "Number of Unique Attendees in Training & Development Sessions (2025)", # included in caption
        x = element_blank(),
        y = "Number of unique attendees") +
  theme_classic() +
  theme(
    title = element_text(size = 14, family="sans"),
    legend.text = element_text(size = 14, family="sans"),
    axis.text = element_text(size = 14, family ="sans"),
    axis.title = element_text(size = 14, family = "sans")
    ) +
  scale_fill_manual(
    values = "#90b8da"
  )
 # scale_x_discrete(
 #   labels = df_label$port_perc_label)


ggsave(plot = last_plot(),filename = here::here("figures", "2025 unique attendance by portfolio.png"),
       width = 15, height = 9, dpi = 300)

```


## Number of Attendees According to their Role

```{r ienrol attendance by role, eval=TRUE}

# count attendees rate by role
df_attend <- df_ienrol_hdr %>%
  filter(attendance_status == "Attended") %>% 
  count(role)

# count unique attendees per portfolio
df_attend_unique_role <- df_ienrol_hdr %>%
  filter(attendance_status == "Attended") %>%
  distinct(fan, attendance_status, role) %>%
  count(role)

```


`r fig_nums(name = "role_attendees", display = "cite")` illustrates the
number of attendees according to their role, as reported in the iEnrol system or 
based on their attendance in HDR supervisor (coded as academics) or HDR student 
training (coded as students).
The majority of attendees were academic staff members
(`r round(df_attend %>% filter(role=="Academic") %>% select(n)/sum(df_attend$n)*100 ,0)`%),
followed by students 
(`r round(df_attend %>% filter(role=="Student") %>% select(n)/sum(df_attend$n)*100 ,0)`%),  
then professional staff members 
(`r round(df_attend %>% filter(role=="Professional") %>% select(n)/sum(df_attend$n)*100 ,0)`%).

An analysis of the unique attendees, indicates that the largest cohort of unique 
attendees were academic staff members (n = `r df_attend_unique_role %>% filter(role=="Academic") %>% select(n)`).

\vskip 0.3in

`r fig_nums(name = "role_attendees")`

```{r plot the ienrol attendance by role, include = TRUE, eval=TRUE, fig.width = 15, fig.height = 9}

# count attendees rate by role
df_attend <- df_ienrol_hdr %>%
  filter(attendance_status == "Attended") %>%
  count(role)

# need to note the threshold for the labels so only the smaller ones are repelled.
threshold <- 100

# plot it [this has attendance numbers by their role, as reported in ienrol]
ggplot(df_attend, aes(
  x = reorder(role, n),
  y = n
)) +
  geom_bar(stat = "identity", colour = "black", fill = "#90b8da") +
  geom_text(aes(y = n,
                x = role,
                label = ifelse(n>threshold, n, "")),
            position = position_stack(vjust = 0.5),
            size = 6) +
  geom_text_repel(aes(y = n,
                      x = role,
                      label = ifelse(n<threshold, n, "")), 
                  box.padding = 0.25,
                  size = 6) +
  coord_flip() +
  labs (#title = "Number of Attendees in Training & Development Sessions (2025)", # included in caption
        x = element_blank(),
        y = "Number of attendees") +
  theme_classic() +
  theme(
    title = element_text(size = 14, family="sans"),
    legend.text = element_text(size = 14, family="sans"),
    axis.text = element_text(size = 14, family ="sans"),
    axis.title = element_text(size = 14, family = "sans")
    ) +
  scale_fill_manual(
    values = "#90b8da"
  )
 # scale_x_discrete(
 #   labels = df_label$port_perc_label)


# ggsave(plot = last_plot(),filename = here::here("figures", "2025 attendance by role.png"),
#        width = 15, height = 9, dpi = 300)

```

\newpage


```{r plot the ienrol attendance for unique attendees by role, include = TRUE, eval=FALSE, fig.width = 15, fig.height = 9}

# count unique attendees per portfolio
df_attend_unique <- df_ienrol_hdr %>%
  filter(attendance_status == "Attended") %>%
  distinct(fan, attendance_status, role) %>%
  count(role)


# plot it [this has unique attendance numbers by the portfolios]
ggplot(df_attend_unique, aes(
  x = reorder(role, n),
  y = n
)) +
  geom_bar(stat = "identity", colour = "black", fill = "#90b8da") +
  geom_text(aes(y = n,
                x = role,
                label = n),
            position = position_stack(vjust = 0.5),
            size = 6) +
  coord_flip() +
  labs (#title = "Number of Unique Attendees in Training & Development Sessions (2025)", # included in caption
        x = element_blank(),
        y = "Number of unique attendees") +
  theme_classic() +
  theme(
    title = element_text(size = 14, family="sans"),
    legend.text = element_text(size = 14, family="sans"),
    axis.text = element_text(size = 14, family ="sans"),
    axis.title = element_text(size = 14, family = "sans")
    ) +
  scale_fill_manual(
    values = "#90b8da"
  )
 # scale_x_discrete(
 #   labels = df_label$port_perc_label)


ggsave(plot = last_plot(),filename = here::here("figures", "2025 unique attendance by portfolio.png"),
       width = 15, height = 9, dpi = 300)

```



\vskip 0.3in

## Differences between activities by Research Development and Support and the Office of Graduate Research

The two teams have historically worked independently serving different cohorts with 
different drivers for their activities. Research Development and Support (RDS) primarily
offers training and development activities to support researchers and research support
staff. Given that their activities are based on a 'value add' approach, they are typically
driven by requests from the research community and by identified areas of need. The 
Office of Graduate Research is primarily focused on ensuring that HDR supervisors meet 
registration requirements, while supporting the development and timely completion of 
HDR students. 

As shown in `r fig_nums(name = "attendee_distributions", display = "cite")`, the OGR
team tends to have more smaller sessions (i.e., between 0-10 attendees) whereas RDS
has more spread across larger numbers (i.e., between 10-20 and 20-30). RDS has more
sessions than OGR with between 50 and 100 attendees, with a few sessions that attract 
more than 100 attendees. 


\vskip 0.3in

```{r plot the sp attendance by team, include = TRUE, eval=TRUE, fig.width = 15, fig.height = 9}

# Bin the 'attended' values into ranges of 10, just to double check the data [hide for now]
# attendees_sp_hdr %>%
#   mutate(attended_bin = cut(attended, breaks = seq(0, 175, by = 10), right = FALSE)) %>%
#   count(team, attended_bin) %>%
#   arrange(team, attended_bin)   

attendees_sp_hdr %>%
  ggplot(aes(x = attended, fill = team)) +
  geom_histogram(breaks = seq(0, 250, by = 10), alpha = 0.5, colour = "black") +
  facet_wrap(~team) + 
  xlab("Attendees (bins of 10)") +
  ylab("Frequency") +
  theme_classic() +
  theme(axis.text = element_text(size = 12), 
        axis.title = element_text(size = 12), 
        strip.text = element_text(size = 14, face = "bold"),
        legend.position = "none") 

```


## Overview of Research Training and Development Topics

Next, we explore the topics of the sessions in more detail. 

The numbers presented in the following tables reflect the total number of attendees
(*n* = `r n_attended_sp_hdr`), most of whom are from Flinders
(*n* = `r nrow(n_attendees_ienrol_hdr)`).



### Delivery Modality: Synchronous vs. Asynchronous

Most of the `r nrow(n_courses_ienrol_hdr)` sessions that we offered in 2025 were 
offered as synchronous sessions 
(n = `r n_courses_ienrol_hdr %>% filter(modality=="synchronous") %>% count()`) 
whereas others were offered as asynchronous
(n = `r n_courses_ienrol_hdr %>% filter(modality=="asynchronous") %>% count()`; typically
as online modules through external providers such as Epigeum). We are 
still cleaning up the HDR data, so we don't yet have the modality information for
all courses; the modality for `r n_courses_ienrol_hdr %>% filter(modality=="to be confirmed") %>% count()`
courses is still to be confirmed. This split in the modality of our sessions reflects
the different approaches used by the two teams; the RDS team offers almost exclusively 
synchronous sessions, whereas the HDR team offers more synchronous sessions to the 
HDR student cohort, as requested in student surveys.

### Delivery Modality: Synchronous vs. Asynchronous

As requested by an academic, the RDS development team has been tracking how many 
people attend hybrid events online vs. in person. We do not have this information for
the HDR events, so this analysis is based on the RDS data only. 

Of the `r nrow(n_courses_rds)` sessions that we offered in 2025, `r nrow(n_event_sp)` 
(`r round((nrow(n_event_sp))/nrow(n_courses_rds)*100, 0)`%)
were held face-to-face, with a hybrid option available whenever possible for those who 
could not attend in person. Unfortunately, it was not possible to offer a hybrid 
option for a few sessions, such as interactive workshops. We will continue to explore 
how to connect with and support our Rural, Regional and Remote colleagues in the future. 
The remainder of the sessions 
(*n* = `r nrow(n_courses_rds)-nrow(n_event_sp)`;`r round(((nrow(n_courses_rds)-nrow(n_event_sp))/(nrow(n_courses_rds))*100),0)`%) 
were offered online through synchronous delivery. 


To better understand our research community's preference for online versus in-person
events, in 2025, we recorded the number of attendees at our hybrid sessions who 
attended in person (*n* = `r sum(n_event_sp$attended_in_person)`;`r round((sum(n_event_sp$attended_in_person))/sum(n_event_sp$attended)*100, 0)`%) 
or online (*n* = `r sum(n_event_sp$attended_online)`; 
`r round((sum(n_event_sp$attended_online))/sum(n_event_sp$attended)*100, 0)`%) . 
Although it is likely that the Flinders' 
research community prefer to meet face-to-face when possible, this in-person 
preference might be inflated by our team's decision to require people to request an 
online link for in-person sessions rather than providing it by default. 

### Themes for Development Programs

`r table_nums(name = "theme_overview", display = "cite")` shows the number
of sessions and attendees by theme. 

The HDR Development team does not use 'development theme' in the same way that the 
RDS team does, so we have grouped their sessions only by audience (HDR students
vs. HDR supervisors). We will work to have more fine-grained information in future
reports. 

The largest number of sessions offered from RDS
was in the 'Research Funding' theme, demonstrating Flinders University's commitment
to support and develop researchers so they can attract external research funding. The fact that this theme
also had the largest number of attendees is evidence that the research community
values these training and development opportunities.

\newpage

```{r theme overview, include = TRUE, eval = TRUE}

#combine sessions & attendees per theme
theme_overview <- df_sp_hdr %>%
  group_by(theme) %>%
  summarise(`Number of Sessions` = n(),
            `Number of Attendees` = sum(attended)) %>%
  arrange (desc(`Number of Attendees`)) %>%
    adorn_totals("row")

# make it look good
kable(theme_overview,
      booktabs = T,
      col.names = c("Theme", "Number of Sessions", "Number of Attendees"),
      align = c('lcc'),
      caption = "Training and Development Summary for 2025",
      linesep = "\\addlinespace") %>%
  kable_styling(latex_options = c("hold_position", "striped"))

```


`r table_nums(name = "sessions_by_theme", display = "cite")` provides
additional detail about the specific sessions that we ran within each of the
training and development themes.

\vskip 0.3in

```{r sessions and attendees by theme, include = TRUE, eval=TRUE}

# how many courses per theme
theme_sessions <- df_sp_hdr %>%
  group_by(theme) %>%
  select(c(theme, course_name, team, modality, attended)) %>%
  arrange(theme, course_name) %>%
  mutate(theme = as.factor(theme))

# make it look good
kable(theme_sessions [, 2:5],
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("Sessions by Themes", "Team", "Modality", "Number of Attendees"),
  caption =
    sprintf("Training and Development Sessions for 2025 (n = %d)",
            n_attended_sp_hdr),
  align = 'lccc',
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(1, width = "3in") %>%
  column_spec(2, width = "1in") %>%
  column_spec(3, width = "1in") %>%
  column_spec(4, width = "1in") %>%
  pack_rows (index = table(theme_sessions$theme),
               latex_gap_space = "0.4em",) %>%
    kable_styling(
    full_width = F,
    latex_options = c("repeat_header", "hold_position", "striped")
  )

```



```{r unique sessions by theme, include = FALSE, eval=FALSE}

# to answer P&C's question of how many unique courses we offer

# how many sessions per theme -- just a quick and dirty report. Copy and paste into excel.

print(unique(df_sp$course_name))

```


\vskip 0.4in

If you have any questions or suggestions for additional researcher training and development
sessions, please contact Dr Jen Beaudry (Manager, Researcher Training, Development
and Communication) in Research Development and Support.
